A highly-available move operation for replicated trees

### 2020-05-05 paper/move-op.tex
Merge the two code figures back into one
Use IEEE journal style

\bibliographystyle{plainurl}
\bibliography{references}{}
\end{document}

>>>>

\section*{Acknowledgements}

The authors wish to acknowledge the support of The Boeing Company and the EPSRC ``REMS: Rigorous Engineering for Mainstream Systems'' programme grant (EP/K008528).
Martin Kleppmann is supported by a Leverhulme Trust Early Career Fellowship and by the Isaac Newton Trust.
Our evaluation was conducted using AWS credits from the AWS Educate program.
Thank you to Marc Shapiro for feedback on a draft of this paper.

\bibliographystyle{IEEEtran}
\bibliography{references}{}
\end{document}
